%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13) 
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
% 
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[ top=1in, bottom=1in, left=.75in,right=.75in]{geometry} % Document margins
\usepackage{tipa}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{fontawesome}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{eurosym}
\pagestyle{fancy}


\lhead{Joshua Meyer}
\rhead{Curriculum Vitae}
%% \cfoot{Page \thepage\ of \pageref{LastPage}}
\cfoot{Page \thepage\ of 4}
\renewcommand{\footrulewidth}{0.4pt}
\setlength{\headheight}{15pt} 
\thispagestyle{empty}

\name{Josh Meyer} % Your name

\begin{document}

\vspace{-.25cm}
\begin{center}
  \href{mailto:joshua.richard.meyer@gmail.com}{\nolinkurl{joshua.richard.meyer@gmail.com}}\\
  \vspace{.15cm}
  \href{https://jrmeyer.github.io}{\textbf{jrmeyer.github.io}} \\
  \vspace{.15cm}
  \href{https://github.com/JRMeyer}{\faGithub} \hspace{.25cm} \href{https://www.linkedin.com/in/josh-r-meyer/}{\faLinkedin} \\

\vspace{.5cm}

\textit{I'm a PhD candidate passionate about Machine Learning and open-source language technologies. \\ My educational background is in Computational Linguistics, Theoretical Linguistics, Natural Language Processing, Statistics, and Cognitive Science. My PhD thesis focuses on Speech Technology, and Automatic Speech Recognition in particular. I work to develop approaches for training more robust Deep Neural Networks for Speech Recognition, using Multi-Task Learning and Transfer Learning. \\ My research is linguistically informed, but based in machine learning methods. }

\vspace{.5cm}

\textit{Currently based in San Francisco.}
\end{center}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
%\begin{minipage}{\textwidth}
\vspace{.5cm}
\begin{rSection}{Education}

{\bf University of Arizona} \hfill {Expected 2019} \\ 
Ph.D. in Linguistics (focus: \textit{computational linguistics}) \hfill {\em Tucson, AZ}

\vspace{.15cm}

{\bf University of Arizona} \hfill {May 2015} \\ 
M.A. in Linguistics \hfill {\em Tucson, AZ}

\vspace{.15cm}

{\bf Seton Hall University} \hfill {May 2012} \\ 
B.A. in Liberal Studies  \hfill {\em South Orange, NJ} \\
%% Summa Cum Laude \\
%% Minor in French \\
%% GPA: 3.92 \\

%% \vspace{.25cm}

%% {\bf Universit\textipa{\"a}t M\textipa{\"u}nster} \hfill {Spring 2010} \\ 
%% Fields of Study: German and French Language \hfill {\em M\textipa{\"u}nster, Germany} \\

\end{rSection}

%\end{minipage}
%----------------------------------------------------------------------------------------

\vspace{.25cm}

\begin{rSection}{Industry Experience}
  
{\bf Mozilla (Machine Learning Research Group)} \hfill {October 2018 --- Present} \\ 
NSF-Sponsored Internship \hfill {} \\
\textit{Developing end-to-end multilingual Automatic Speech Recognition techniques} \hfill {} \\
\textit{based on Transfer Learning and Deep Neural Networks (i.e. DeepSpeech).} \hfill {} \\
  
{\bf Various Companies} \hfill {2016 --- 2018} \\ 
Kaldi \& ASR Consultant  \hfill {} \\
\textit{Optimized Automatic Speech Recognition pipelines}   \hfill {} \\
\textit{for various companies using the Kaldi toolkit.}   \hfill {} \\

\end{rSection}




%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------
\begin{minipage}{\textwidth}

\begin{rSection}{Technical Strengths}
\vspace{.25cm}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Python, Bash, \textsc{MATLAB}, Perl, R, C++ (\textit{some knowledge}) \\
Other & TensorFlow, Kaldi, Linux, Amazon Web Services, git \& GitHub \\
\end{tabular}
\end{rSection}

\end{minipage}
%------------------------------------------------------------------------


\newpage


%----------------------------------------------------------------------------------------

\vspace{.25cm}

\begin{rSection}{Open Source Work}

  {\textbf{Mozilla DeepSpeech}} {\hfill \textit{Added Transfer Learning branch} {\hspace{2.5cm} \href{https://github.com/mozilla/DeepSpeech/tree/transfer-learning}{\textbf{[Code]}}}} \\
\vspace{-.35cm}

{\textbf{NVDA}} {\hfill \textit{Added Kyrgyz language to screen reader} {\hspace{2.5cm} \href{https://github.com/JRMeyer/nvda}{\textbf{[Code]}}}} \\
\vspace{-.35cm}

{\textbf{eSpeak NG}} {\hfill \textit{Added Kyrgyz language to speech synthesizer} {\hspace{2.5cm} \href{https://github.com/rhdunn/espeak/commits?author=JRMeyer}{\textbf{[Code]}}}}\\
\vspace{-.35cm}

{\textbf{Autotrace}} {\hfill \textit{Created tools for tongue contour visualization} {\hspace{2.5cm} \href{https://github.com/JRMeyer/Autotrace}{\textbf{[Code]}}}} \\

\end{rSection}



%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
%\begin{minipage}{\textwidth}
\vspace{.25cm}

\begin{rSection}{Research Experience}

\begin{rSubsection}{National Science Foundation}{July 2015 --- Present}{Graduate Research Fellow}{}
\item Conducting PhD thesis research on Multi-Task Learning and Deep Learning techniques for Automatic Speech Recognition in low-resource data scenarios
\end{rSubsection}


\begin{rSubsection}{CNRS-LIMSI}{July 2016 --- July 2017}{Chateaubriand Research Fellow}{Orsay, France}
\item DNN acoustic model adaptation and RNN text augmentation techniques
\end{rSubsection}

\begin{rSubsection}{American University of Central Asia}{June 2015 --- August 2015}{Visiting Research Scholar}{Bishkek, Kyrgyzstan}
\item Created a spoken corpus of the Kyrgyz language
\end{rSubsection}
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Arizona Phonological Imaging Lab}{Spring 2015}{Research Assistant}{Tucson, AZ}
\item Developed software to process ultrasonic images
\end{rSubsection}
%----------------------------------------------------------------------------------------

\begin{rSubsection}{American University of Central Asia}{August 2013 --- March 2014}{Visiting Research Fellow}{Bishkek, Kyrgyzstan}
\item Conducted acoustic-phonetic and phonological research
\end{rSubsection}
%----------------------------------------------------------------------------------------

%% \begin{rSubsection}{Arizona Scottish Gaelic Project}{September 2012 - July 2013}{Research Assistant}{Tucson, AZ}
%% \item Conducted fieldwork with speakers of Scottish Gaelic; Aided in online grammar compilation
%% \end{rSubsection}
%% %----------------------------------------------------------------------------------------

\begin{rSubsection}{Language Acquisition Research Center at Hunter CUNY}{November 2011 --- August 2012}{Research Assistant}{New York, NY}
\item Transcribed spontaneous speech; Aided in website construction
\end{rSubsection}
%----------------------------------------------------------------------------------------

\begin{rSubsection}{KIT/NYU MEG Lab at NYU}{May 2012 --- August 2012}{Research Assistant}{New York, NY}
\item Aided in data analysis and processing
\end{rSubsection}
%----------------------------------------------------------------------------------------

\begin{rSubsection}{Language Acquisition and Neurolinguistics Lab at Rutgers}{May 2012 - August 2012}{Research Assistant}{New Brunswick, NJ}
\item Aided in experiment design
\end{rSubsection}

\end{rSection}

%\end{minipage}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	GRANTS AND FELLOWSHIPS SECTION
%----------------------------------------------------------------------------------------
\vspace{.25cm}

\begin{minipage}{\textwidth}

\begin{rSection}{Grants \& Awards}
  \vspace{.15cm}
  

%----------------------------------------------------------------------------------------
%\begin{rSubsection}{CoLang Fellowship}{Summer 2014}{\$375 (Declined)}{Linguistics Society of America}
%\item
%\end{rSubsection}
%----------------------------------------------------------------------------------------

{\bf NSF INTERN Grant} \hfill {2018} \\ 
{\em Approx. \${50,000}} \hfill {\em National Science Foundation} \\

%----------------------------------------------------------------------------------------

{\bf Chateaubriand STEM Fellowship} \hfill {2016} \\ 
{\euro{5.000}} \hfill {\em French Embassy to the United States of America} \\

%----------------------------------------------------------------------------------------

{\bf GROW Travel Award} \hfill {2016} \\ 
{\$5,000} \hfill {\em National Science Foundation} \\

%----------------------------------------------------------------------------------------

{\bf Graduate Research Fellowship} \hfill {2015-2018} \\ 
{\em Approx. \$102,000 + \$36,000 (tuition)} \hfill {\em National Science Foundation} \\

%----------------------------------------------------------------------------------------

%% {\bf Graduate Tuition \& Fees Waver} \hfill {2012-2013 \& 2014-2015} \\ 
%% {\em Approx. \$50,000} \hfill {\em Linguistics Department, University of Arizona} \\

%% %----------------------------------------------------------------------------------------

{\bf Visiting Research Fellowship} \hfill {August 2013 --- March 2014} \\ 
{\em \$5,000} \hfill {\em Central Asian Studies Institute, American University of Central Asia} \\

%----------------------------------------------------------------------------------------

{\bf Regents Scholarship} \hfill {August 2008 --- May 2012} \\ 
{\em \$111,140 (tuition)} \hfill {\em Seton Hall University} \\

%----------------------------------------------------------------------------------------

%% {\bf Liberal Studies Honors Citation} \hfill {May 2012} \\ 
%% {\null} \hfill {\em Seton Hall University} \\

\end{rSection}
\end{minipage}
%----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{\textwidth}

  \begin{rSection}{Publications}
    \vspace{.25cm}


      {(2018)} {Meyer, Joshua.} {\bf Unsupervised Task Discovery for Multi-Task Acoustic Modeling.} {Proceedings of the Machine Learning in Speech and Language Processing Workshop.} {\href{https://github.com/JRMeyer/mlslp/blob/master/poster/mlslp-poster.pdf}{[Poster]}} {\href{https://sites.google.com/view/mlslp/proceedings}{[Paper]}} \\  

          {(2018)} {Meyer, Joshua, and Kloehn, Nick, and Carnie, Andrew.} {\href{https://www.degruyter.com/view/product/481684}{\bf{The Field is not the Lab, and the Lab is not the Field: Experimental linguistics and endangered language communities.}}} {{\it Insights from Practices in Community-Based Research: From Theory To Practice Around The Globe, ISBN: 978-3-11-052701-8} Edited by Shannon Bischoff and Carmen Jany. \textit{Mouton De Gruyter}}\\


        {(2018)} {Bekmurzaev, Nurbek, and Lottholz, Philipp, and Meyer, Joshua.} {\href{https://www.tandfonline.com/doi/abs/10.1080/02634937.2017.1419165}{\textbf{Navigating the safety implications of doing research and being researched in Kyrgyzstan: cooperation, networks and framing.}}} {\textit{Central Asian Survey, 37:1, 100-118, DOI: 10.1080/02634937.2017.1419165}}\\
        
        {(2017)} {Meyer, Joshua.} {\href{http://www.turklang.tatar/wp-content/uploads/2017/05/TurkLang-2017.-Tom1.pdf}{{\bf Development of a Kyrgyz Speech Synthesizer: A Demonstration of the Ossian Frontend and Merlin Neural Network Speech Synthesis Toolkit.}}} {\textit{Proceedings of The 5th International Conference on Computer Processing of Turkic Languages, Vol. 1, 130-136}.}\\ 

        {(2016)} {Lottholz, Philipp, and Meyer, Joshua.} { \href{https://blogs.exeter.ac.uk/excas/2016/04/14/friend-or-foreign-agent-on-the-limits-of-field-research-in-post-soviet-kyrgyzstan/}{\bf ‘Friend’ or ‘Foreign Agent’? On the Limits of Field Research in Post-Soviet Kyrgyzstan.}} {\textit{Exeter Central Asian Studies Network}.}\\
 
        {(2016)} {Meyer, Joshua.} { \href{https://journals.uair.arizona.edu/index.php/arizanthro/article/viewFile/21375/20949}{\bf Conducting Linguistic Fieldwork in Kyrgyzstan.}} {\textit{Arizona Anthropologist}, Vol. 27.}   \\  

\end{rSection}

\end{minipage}
%----------------------------------------------------------------------------------------




%----------------------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------
%\begin{minipage}{\textwidth}

\begin{minipage}{\textwidth}

\begin{rSection}{Presentations}
\vspace{.25cm}

  {\bf Language Technologies in Central Asia: A Survey.} {Joint ESCAS-CESS Conference at the American University of Central Asia.} \hfill {\em 2017, Bishkek} \\
  
{\bf Predicting Language Dominance in Kyrgyz-Russian Bilinguals.} {w/ Quam, Carolyn} {Arizona Linguistics Circle 9.} \hfill {\em 2015, Tucson} \\

{\bf Phonological processing in Kyrgyz-Russian bilinguals.} {w/ Quam, Carolyn, and Bever, Thomas}  {The Miniconference on Metrical Structure: Acquisition and processing.} \hfill {\em 2014, Utrecht} \\

{\bf The Kyrgyzstan corpus project: Building a language resource unique to Kyrgyzstan and available to all.} {CASI Public Seminar at the American University of Central Asia.} \hfill {\em 2014, Bishkek} \\

{\bf Now you hear it, now you don’t: Phonological processing in Kyrgyz-Russian bilinguals.} {CASI Public Seminar at the American University of Central Asia.} \hfill {\em 2013, Bishkek} \\

{\bf Psycholinguistics: Thinking about language differently.} {Lecture conducted at The Platttform at Werkstatttraum.} \hfill {\em 2013, Berlin} \\


\end{rSection}
\end{minipage}


\begin{minipage}{\textwidth}
\begin{rSection}{Event Organizaion}
\vspace{.25cm}

  {\bf Kyrgyz Voice Technology Hackathon} {Attended by undergraduate students as well as professional developers.} {\em (2019, American University of Central Asia)} \hfill {\href{https://jrmeyer.github.io/kyrgyz-voice-hackathon/}{\textbf{[Link]}}} \\
  
  {\bf DeepSpeech \& Common Voice Tutorial}   {Delivered to attendees of the Fifth International Workshop on Computational Linguistics for Uralic Languages.}  {\em (2019, University of Tartu)} \hfill { \href{https://sisu.ut.ee/iwclul2019/avaleht}{\textbf{[Link]}}}  \\

  {\bf Speech Synthesis Workshop: Hands-on with Merlin \& Ossian}   {Delivered to Computational Linguistics Faculty and Graduate Students.} {\em (2018, Higher School of Economics)} \hfill  {\href{http://jrmeyer.github.io/tts/2016/12/09/tts-workshop.html}{\textbf{[Link]}}} \\

  {\bf Speech Recognition Workshop: Hands-on with Kaldi \& DeepSpeech} {Delivered to Computational Linguistics Faculty and Graduate Students.} {\em (2017, Higher School of Economics)} \hfill  {\href{http://jrmeyer.github.io/misc/stt-vishka.pdf}{\textbf{[Link]}}}\\

\end{rSection}
\end{minipage}
%----------------------------------------------------------------------------------------



%% %----------------------------------------------------------------------------------------
%% %	TEACHING EXPERIENCE SECTION
%% %----------------------------------------------------------------------------------------
%% %\begin{minipage}{\textwidth}
%% \vspace{.25cm}

%% \begin{rSection}{Teaching}

%% \begin{rSubsection}{Mind, Self \& Language (LING 150)}{Spring 2015 \& Fall 2014}{Teaching Assistant}{University of Arizona}
%% \item
%% %% \item Conducted weekly discussion section
%% %% \item Graded assignments
%% \end{rSubsection}

%% \begin{rSubsection}{Language Development (LING/PSY/SLHS 341)}{Fall 2014}{Teaching Assistant}{University of Arizona}
%% \item 
%% %% \item Delivered select lectures
%% %% \item Graded assignments
%% \end{rSubsection}

%% \end{rSection}
%% %\end{minipage}
%% %----------------------------------------------------------------------------------------



%----------------------------------------------------------------------------------------


%% %----------------------------------------------------------------------------------------
%% %	VOLUNTEER EXPERIENCE
%% %----------------------------------------------------------------------------------------
%% %\begin{minipage}{\textwidth}

%% \begin{rSection}{Volunteer Experience}

%% \begin{rSubsection}{Oasis Kyrgyzstan}{Fall 2013 - Spring 2014}{EFL Teacher}{Bishkek, Kyrgyzstan}
%% \item Conducted English talking club once a week for teenagers
%% \end{rSubsection}
%% %----------------------------------------------------------------------------------------


%% \begin{rSubsection}{Orion Russian Foster Community}{Summer 2009/2011}{EFL Teacher}{Kaluga Oblast, Russian Federation}
%% \item Taught two classes daily
%% \item Created lesson plans
%% \item Assessed language skills of children and placed them into classes accordingly
%% \item Recorded progress and reported to school administrator
%% \end{rSubsection}
%% %----------------------------------------------------------------------------------------

%% \begin{rSubsection}{Seton Hall University Division of Volunteer Efforts}{Spring 2009 \& Fall 2011}{ESL Assistant}{South Orange, NJ}
%% \item Served as a teacher's assistant for adult education
%% \item Tailored existing lesson plans to needs of individual students
%% \item Reported progress to program director
%% \end{rSubsection}
%% %----------------------------------------------------------------------------------------

%% \begin{rSubsection}{Y\textipa{\'e}le Haiti Donation Center}{Fall 2010}{Volunteer}{South Orange, NJ}
%% \item Directed teams of volunteers in packaging and donation reception
%% \item Performed administrative tasks
%% \end{rSubsection}
%% %----------------------------------------------------------------------------------------

%% \end{rSection}
%% %\end{minipage}
%% %----------------------------------------------------------------------------------------



\begin{minipage}{\textwidth}
\begin{rSection}{Written Tutorials}
  \vspace{.25cm}

  {How to Train \textit{practically} any Model from \textit{practically} any Data with TensorFlow} \hfill \href{http://jrmeyer.github.io/machinelearning/2019/05/29/tensorflow-dataset-estimator-api.html}{\textbf{[Link]}}% \hfill {May, 2018}

    \vspace{.25cm}

  {Getting started with the Merlin Speech Synthesis Toolkit} \hfill  \href{http://jrmeyer.github.io/tts/2017/02/14/Installing-Merlin.html}{\textbf{[Link]}}%\hfill {February, 2017}
    \vspace{.25cm}
  
  {How to Train a Deep Neural Net Acoustic Model with Kaldi} \hfill \href{http://jrmeyer.github.io/asr/2016/12/15/DNN-AM-Kaldi.html}{\textbf{[Link]}}% \hfill {December, 2016}
    \vspace{.25cm}

  {How to add a new language to the eSpeak NG Speech Synthesizer} \hfill \href{http://jrmeyer.github.io/tts/2016/07/03/How-to-Add-a-Language-to-eSpeak-NG.html}{\textbf{[Link]}}% \hfill {July, 2016}
    \vspace{.25cm}

  {The Flow of TensorFlow: An Email Classification Tutorial} \hfill \href{http://jrmeyer.github.io/machinelearning/2016/02/01/TensorFlow-Tutorial.html}{\textbf{[Link]}}%\hfill {February, 2016}
    \vspace{.25cm}

  {An Introduction to CMU-Sphinx Speech Recognition Toolkit: First Steps}  \hfill \href{http://jrmeyer.github.io/asr/2016/01/09/Installing-CMU-Sphinx-on-Ubuntu.html}{\textbf{[Link]}}%\hfill {January, 2016}
 
\end{rSection}
\end{minipage}
\end{document}


















%----------------------------------------------------------------------------------------
%	CROSS-CULTURAL EXPERIENCE
%----------------------------------------------------------------------------------------
%\begin{minipage}{\textwidth}
%
%\begin{rSection}{Cross-Cultural Experience}
%
%\tabulinesep=1.5mm
%\begin{tabu} to \textwidth {X[l]
%                           X[l]
%                           X[l]}
%                           
%\textbf{Kyrgyzstan} & Visiting Scholar & 7.5 Months \\
%\textbf{Russia} & Volunteer in village of foster families & 6 Months \\
%\textbf{Germany} & Exchange student & 4 Months \\
%\textbf{France} & WWOOF & 3 Months \\
%\textbf{Ukraine} & WWOOF & 2 weeks \\
%\textbf{Kazakhstan} & Travel & 1 week \\
%\textbf{Philippines, Malaysia, Singapore} & Travel & 1 Month \\
%\textbf{Turkey, Greece, Macedonia, Kosovo, Montenegro, Albania, Bosnia, Serbia} & Travel & 2 weeks \\
%
%\end{tabu}
%\end{rSection}
%
%\end{minipage}
%%------------------------------------------------------------------------
%


%----------------------------------------------------------------------------------------
%	LANGUAGE SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{minipage}{\textwidth}

\begin{rSection}{Language Skills}
\vspace{.25cm}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Native & English \\                  
Fluent & Russian, French \\
Some Knowledge & German, Spanish, Italian, Kyrgyz \\
\end{tabular}

\end{rSection}

\end{minipage}
%------------------------------------------------------------------------
